An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-11 paper.tex
Fixed a bunch of spelling.

\begin{description}
  \item[analog-channel-map] A mapping of the strings D-Flow assigns to signals
    emmitted from the analog channels of the NI USB-6255 to names the user
    desires.
  \item[cortex-version] The version of Cortex used to record the trial.
  \item[datetime]A date formatted string giving the date of the trial in the
    \verb|YYYY-MM-DD| format.
  \item[dflow-version] The version of D-Flow used to record the trial.
  \item[events] A key value map which prescribes names to the alphabetic events
    recorded in the record file.
  \item[files] A key value mapping of files associated with this trial
    where the key is the DFlow file type and the value is the path to the file
    relative to the meta file.
  \item[hardware-settings] There are tons of settings for the hardware in both
    D-Flow, Cortex, and the other software in the system. This contains any
    non-default settings.
    \begin{description}
      \item[high-performance] A boolean value indicatin whether the D-Flow high
        performance setting was on (True) or off (False).
    \end{description}
  \item[id] An unique three digit integer identifier for the trial. All of the
    file names and directories associated with this trial include this number.
  \item[marker-map] A key value map which maps marker names in the mocap file
    to the user's desired names for the markers.
  \item[marker-set] Indicates the HBM~\cite{Bogert2013} marker set used during
    the trial, either full, lower, or NA.
  \item[nominal-speed] A float representing the nominal desired treadmill speed
    during the trial.
  \item[nominal-speed-units] (string) The units of the nominal speed.
  \item[notes] Any notes about the trial.
  \item[pitch] A boolean that indicates if the treamdill pitch degree of
    freedom was acutated during the trial.
  \item[stationary-platform] A boolean that indicates whether the treadmill
      sway or pitch motion was actuated during the trial. If this flag is
      false, the measured ground reaction forces must be compensated for the
      inertial affects and be expressed in the motion capture reference frame.
  \item[subject-id] An integer corresponding to the subject in the trial.
  \item[sway] A boolean that indicates if the treadmill lateral (sway) degree
    of freedom was acutated during the trial.
\end{description}

\begin{listing*}
  \small
  \begin{minted}[gobble=4]{yaml}
    study:
       id: 1
       name: Gait Control Identification
       description: Perturb the subject during walking and running.
    subject:
       id: 8
       age: 20
       mass: 70.0
       mass-units: kilograms
       height: 1.572
       height-units: meters
       knee-width-left: 107.43
       knee-width-right: 107.41
       knee-width-units: millimeters
       ankle-width-left: 70.52
       ankle-width-right: 67.66
       ankle-width-units: millimeters
       gender: male
    trial:
       id: 58
       subject-id: 8
       datetime: 2014-03-28
       notes: >
           The subject did a somersault during this trial instead of following
           instructions to walk. Will have to use for another study.
       nominal-speed: 0.8
       nominal-speed-units: meters per second
       stationary-platform: True
       pitch: False
       sway: False
       hardware-settings:
           high-performance: True
       dflow-version: 3.16.1
       cortex-version: 3.1.1.1290
       marker-map:
           M1: LHEAD
           M2: THEAD
           M3: RHEAD
           M4: FHEAD
           M5: C7
       analog-channel-map:
           Channel1.Anlg: F1Y1
           Channel2.Anlg: F1Y2
           Channel3.Anlg: F1Y3
           Channel4.Anlg: F1X1
       events:
           A: Force Plate Zeroing
           B: Calibration Pose
           C: First Normal Walking
           D: Longitudinal Perturbation
           E: Second Normal Walking
           F: Unloaded End
       files:
           compensation: ../T057/mocap-057.txt
           mocap: mocap-058.txt
           record: record-058.txt
           meta: meta-058.yml
  \end{minted}
  \caption{A fictious example of a YAML formatted meta data file. All of the
    possible keys in the data set are shown.}
  \label{lis:example-meta-data}
\end{listing*}

>>>>

\begin{description}
  \item[analog-channel-map] A mapping of the strings D-Flow assigns to signals
    emitted from the analog channels of the NI USB-6255 to names the user
    desires.
  \item[cortex-version] The version of Cortex used to record the trial.
  \item[datetime]A date formatted string giving the date of the trial in the
    \verb|YYYY-MM-DD| format.
  \item[dflow-version] The version of D-Flow used to record the trial.
  \item[events] A key value map which prescribes names to the alphabetic events
    recorded in the record file.
  \item[files] A key value mapping of files associated with this trial
    where the key is the D-Flow file type and the value is the path to the file
    relative to the meta file.
  \item[hardware-settings] There are tons of settings for the hardware in both
    D-Flow, Cortex, and the other software in the system. This contains any
    non-default settings.
    \begin{description}
      \item[high-performance] A boolean value indicating whether the D-Flow high
        performance setting was on (True) or off (False).
    \end{description}
  \item[id] An unique three digit integer identifier for the trial. All of the
    file names and directories associated with this trial include this number.
  \item[marker-map] A key value map which maps marker names in the mocap file
    to the user's desired names for the markers.
  \item[marker-set] Indicates the HBM~\cite{Bogert2013} marker set used during
    the trial, either full, lower, or NA.
  \item[nominal-speed] A float representing the nominal desired treadmill speed
    during the trial.
  \item[nominal-speed-units] (string) The units of the nominal speed.
  \item[notes] Any notes about the trial.
  \item[pitch] A boolean that indicates if the treadmill pitch degree of
    freedom was actuated during the trial.
  \item[stationary-platform] A boolean that indicates whether the treadmill
      sway or pitch motion was actuated during the trial. If this flag is
      false, the measured ground reaction forces must be compensated for the
      inertial affects and be expressed in the motion capture reference frame.
  \item[subject-id] An integer corresponding to the subject in the trial.
  \item[sway] A boolean that indicates if the treadmill lateral (sway) degree
    of freedom was actuated during the trial.
\end{description}

\begin{listing*}
  \small
  \begin{minted}[gobble=4]{yaml}
    study:
       id: 1
       name: Gait Control Identification
       description: Perturb the subject during walking and running.
    subject:
       id: 8
       age: 20
       mass: 70.0
       mass-units: kilograms
       height: 1.572
       height-units: meters
       knee-width-left: 107.43
       knee-width-right: 107.41
       knee-width-units: millimeters
       ankle-width-left: 70.52
       ankle-width-right: 67.66
       ankle-width-units: millimeters
       gender: male
    trial:
       id: 58
       subject-id: 8
       datetime: 2014-03-28
       notes: >
           The subject did a somersault during this trial instead of following
           instructions to walk. Will have to use for another study.
       nominal-speed: 0.8
       nominal-speed-units: meters per second
       stationary-platform: True
       pitch: False
       sway: False
       hardware-settings:
           high-performance: True
       dflow-version: 3.16.1
       cortex-version: 3.1.1.1290
       marker-map:
           M1: LHEAD
           M2: THEAD
           M3: RHEAD
           M4: FHEAD
           M5: C7
       analog-channel-map:
           Channel1.Anlg: F1Y1
           Channel2.Anlg: F1Y2
           Channel3.Anlg: F1Y3
           Channel4.Anlg: F1X1
       events:
           A: Force Plate Zeroing
           B: Calibration Pose
           C: First Normal Walking
           D: Longitudinal Perturbation
           E: Second Normal Walking
           F: Unloaded End
       files:
           compensation: ../T057/mocap-057.txt
           mocap: mocap-058.txt
           record: record-058.txt
           meta: meta-058.yml
  \end{minted}
  \caption{A fictitious example of a YAML formatted meta data file. All of the
    possible keys in the data set are shown.}
  \label{lis:example-meta-data}
\end{listing*}
